Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-27 article.tex
wording
section 4: precision filtering GENIE3 et PC

In the bottom of Table \ref{tab:comparison}, we provide as a comparison the
performance of three other methods: standard (Pearson) correlation (PC),
generalized transfer entropy (GTE), and GENIE3. ROC and PR curves on the
\textit{normal-2} network are shown for all methods in Figure
\ref{fig:curves}. Pearson correlation measures the unconditional linear
(in)dependence between variables and it should thus not be able to filter out
indirect interactions between neurons. GTE \citep{stetter2012model} was
proposed as a baseline for the challenge. This method builds on Transfer
Entropy to measure the association between two neurons. Unlike our approach, it
can predict the direction of the edges. GENIE3 \citep{huynhthu2010inferring} is
a gene regulatory network inference method that was the best performer of the
DREAM5 challenge \citep{marbach2012}. When transposed to neural networks, this
method uses as a confidence score for the edge going from neuron $i$ to neuron
$j$ the importance score of variable $X_i$ in a Random Forest model trying to
predict $X_j$ from all variables in $X\setminus X_j$. To reduce the
computational cost of this method, we had however to limit each tree in the
Random Forest model to a maximum depth of 3. This constraint potentially
severely affects the performance of this method with respect to the use of fully
grown trees. We nevertheless provide these results for comparison purpose. PC
and GENIE3 were both applied on the same pre-filtered time series as partial
correlation ($h\circ g \circ f_1$). For GENIE3, we built 10000 trees per neuron
and we used default settings for all other parameters (except for the maximal
tree depth). For GTE, we reproduced the exact same setting (conditioning level
and pre-processing) that was used for the challenge.

>>>>

In the bottom of Table \ref{tab:comparison}, we provide as a comparison the
performance of three other methods: standard (Pearson) correlation (PC),
generalized transfer entropy (GTE), and GENIE3. ROC and PR curves on the
\textit{normal-2} network are shown for all methods in Figure
\ref{fig:curves}. Pearson correlation measures the unconditional linear
(in)dependence between variables and it should thus not be able to filter out
indirect interactions between neurons. GTE \citep{stetter2012model} was
proposed as a baseline for the challenge. This method builds on Transfer
Entropy to measure the association between two neurons. Unlike our approach, it
can predict the direction of the edges. GENIE3 \citep{huynhthu2010inferring} is
a gene regulatory network inference method that was the best performer of the
DREAM5 challenge \citep{marbach2012}. When transposed to neural networks, this
method uses as a confidence score for the edge going from neuron $i$ to neuron
$j$ the importance score of variable $X_i$ in a Random Forest model trying to
predict $X_j$ from all variables in $X\setminus X_j$. To reduce the
computational cost of this method, we had however to limit each tree in the
Random Forest model to a maximum depth of 3. This constraint potentially
severely affects the performance of this method with respect to the use of
fully grown trees. PC and GENIE3 were applied on the time series filtered using
respectively the functions $w\circ h\circ g$ and $h\circ g\circ f_1$ (which
gave the best performance). For GENIE3, we built 10000 trees per neuron and we
used default settings for all other parameters (except for the maximal tree
depth). For GTE, we reproduced the exact same setting (conditioning level and
pre-processing) that was used by the challenge organizers.
